The \dealii{} Library, Version 9.3

### 2021-06-21 9.3/paper.tex
More minor edits.

The new \texttt{step-76} tutorial program illustrates this latter case
in the context of the solution of the Euler equations. \texttt{step-76} reaches a
speed-up of 27\% compared to the
original version, \texttt{step-67}, by using the new feature.
For more details and the usage of the feature in the library \texttt{hyper.deal}, see \citep{munch2020hyperdeal}.

@@

To give an example of the new features, let us consider the evaluation of a
surface tension force in the context of sharp-interface methods, whose
contribution is added to a fluid solver by multiplication with test function
and addition over quadrature points located at the interface section
$\Gamma_K=\Gamma \cup K$ located on the current cell $K$ and that is,
in general, located differently within $K$ than for any other cell:
\begin{align*}
\left(\mathbf{v}, \kappa \, \mathbf{n}\right)_\Gamma
\approx
\sum_q \mathbf{v}(\mathbf{x}_q) \cdot \left(\kappa(\mathbf{x}_q) \, \mathbf{n}(\mathbf{x}_q)\right) (JxW)_q.
\end{align*}
In \dealii{}, this can now be conveniently written as
\begin{c++}
phi_curvature.reinit(cell, reference_points);
phi_normal.reinit(cell, reference_points);
phi_force.reinit(cell, reference_points);

@@

There is also a new program in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and intended as starting points for further
research rather than as teaching tools):
\begin{itemize}
\item ``\texttt{Laplace equation coupled to an external simulation program}'' was
  contributed by David Schneider and Benjamin Uekermann at Technical University
  of Munich. It shows by extending \texttt{step-4}---a time-dependent Poisson
  problem~---how to surface-couple a \dealii application with a simple external 
  application, using the \texttt{preCICE} 
  library~\cite{bungartz2016precice, lindner2020exafsa}. \texttt{preCICE},
  however, also allows to couple \dealii to actual external simulation softwares, 
  such as OpenFOAM, SU2, CalculiX, or FEniCS, using provided adapter classes. 
  For more details visit their webpage
  \url{https://precice.org/} and check out the numerous \dealii tutorials there,
  showing, i.a., interesting fluid-structure interaction application cases.
\end{itemize}

>>>>

The new \texttt{step-76} tutorial program illustrates this case
in the context of the solution of the Euler equations. It reaches a
speed-up of 27\% compared to the
original version, \texttt{step-67}, by using the new feature.
For more details and the usage of the feature in the library \texttt{hyper.deal}, see \citep{munch2020hyperdeal}.

@@

As an example, let us consider the evaluation of a
surface tension force in the context of sharp-interface methods, whose
contribution is added to a fluid solver by multiplication with test function
and addition over quadrature points located at the interface section
$\Gamma_K=\Gamma \cup K$ of the current cell $K$ and that is,
in general, positioned differently within $K$ than for any other cell:
\begin{align*}
\left(\mathbf{v}, \kappa \, \mathbf{n}\right)_\Gamma
\approx
\sum_q \mathbf{v}(\mathbf{x}_q) \cdot \left(\kappa(\mathbf{x}_q) \, \mathbf{n}(\mathbf{x}_q)\right) (JxW)_q.
\end{align*}
In \dealii{}, this can now be conveniently written as
\begin{c++}
phi_curvature.reinit(cell, reference_points);
phi_normal.reinit(cell, reference_points);
phi_force.reinit(cell, reference_points);

@@

There is also a new program in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and intended as starting points for further
research rather than as teaching tools):
\begin{itemize}
\item ``\texttt{Laplace equation coupled to an external simulation program}'' was
  contributed by David Schneider and Benjamin Uekermann at Technical University
  of Munich. It extends \texttt{step-4} to a time-dependent Poisson
  problem and couples it with a simple external surface-based
  application, using the \texttt{preCICE} 
  library~\cite{bungartz2016precice, lindner2020exafsa}. \texttt{preCICE},
  also allows to couple \dealii to external simulation packages, 
  such as OpenFOAM, SU2, CalculiX, or FEniCS, using adapter classes. 
  The webpage
  \url{https://precice.org/} provides several more \dealii{}-based tutorials,
  including interesting fluid-structure interaction applications.
\end{itemize}
